{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Models for detecting BHBH, BHNS and NSNS binaries with LISA

### 2021-11-23 paper/tex/sections/appendix.tex
update table and other comments

        A & Fiducial & \confinv{124}{11}{11} & \confinv{74}{9}{9} & \confinv{42}{6}{7} & \confinv{8}{3}{3} & \confinv{202}{14}{14} & \confinv{118}{11}{11} & \confinv{71}{8}{9} & \confinv{13}{4}{4}\\
        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{94}{10}{10} & \confinv{69}{8}{8} & \confinv{22}{4}{5} & \confinv{3}{2}{2} & \confinv{149}{12}{13} & \confinv{108}{11}{10} & \confinv{37}{6}{6} & \confinv{5}{2}{2}\\
        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{59}{8}{8} & \confinv{47}{7}{7} & \confinv{8}{3}{3} & \confinv{4}{2}{2} & \confinv{96}{10}{10} & \confinv{76}{9}{9} & \confinv{14}{4}{3} & \confinv{6}{2}{3}\\
        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{67}{8}{8} & \confinv{47}{7}{7} & \confinv{7}{2}{3} & \confinv{13}{4}{3} & \confinv{104}{10}{11} & \confinv{71}{8}{9} & \confinv{12}{3}{4} & \confinv{21}{4}{5}\\
        E & No Case BB mass transfer systems & \confinv{77}{9}{8} & \confinv{69}{8}{9} & \confinv{7}{2}{3} & \boldconfinv{0}{0}{1} & \confinv{121}{11}{11} & \confinv{109}{10}{11} & \confinv{12}{4}{3} & \boldconfinv{0}{0}{1} \\
        F & Case BB Unstable + Optimistic CE & \boldconfinv{321}{18}{18} & \boldconfinv{154}{12}{13} & \boldconfinv{148}{12}{13} & \confinv{18}{4}{4} & \boldconfinv{484}{22}{22} & \boldconfinv{240}{16}{15} & \confinv{217}{15}{15} & \confinv{27}{5}{6}\\
        G & CE efficiency $\alpha = 0.1$ & \confinv{40}{6}{7} & \confinv{28}{5}{5} & \boldconfinv{2}{1}{2} & \confinv{10}{3}{3} & \confinv{64}{8}{8} & \confinv{44}{7}{7} & \boldconfinv{3}{1}{2} & \confinv{17}{4}{4}\\
        H & CE efficiency $\alpha = 0.5$ & \confinv{86}{9}{9} & \confinv{58}{7}{8} & \confinv{22}{5}{4} & \confinv{6}{3}{2} & \confinv{136}{11}{12} & \confinv{92}{10}{9} & \confinv{35}{6}{6} & \confinv{10}{3}{3}\\
        I & CE efficiency $\alpha = 2.0$ & \confinv{133}{11}{12} & \confinv{68}{9}{8} & \confinv{38}{6}{6} & \confinv{28}{6}{5} & \confinv{218}{14}{15} & \confinv{110}{11}{10} & \confinv{63}{8}{8} & \confinv{46}{7}{7}\\
        J & CE efficiency $\alpha = 10.0$ & \confinv{78}{9}{9} & \confinv{27}{5}{5} & \confinv{16}{4}{4} & \boldconfinv{35}{6}{6} & \confinv{126}{11}{11} & \confinv{42}{6}{7} & \confinv{27}{6}{5} & \boldconfinv{57}{7}{8}\\
        K & HG donor stars initiating a CE survive CE & \confinv{218}{15}{15} & \confinv{152}{13}{12} & \confinv{57}{8}{7} & \confinv{10}{3}{3} & \confinv{341}{18}{19} & \confinv{230}{15}{15} & \confinv{96}{10}{10} & \confinv{16}{4}{4}\\
        L & Fryer rapid SN remnant mass prescription & \confinv{127}{11}{12} & \confinv{50}{7}{7} & \confinv{70}{8}{9} & \confinv{7}{3}{2} & \confinv{205}{14}{14} & \confinv{77}{9}{8} & \confinv{117}{10}{11} & \confinv{11}{3}{3}\\
        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{133}{11}{12} & \confinv{96}{10}{10} & \confinv{30}{5}{6} & \confinv{7}{2}{3} & \confinv{215}{14}{15} & \confinv{154}{13}{12} & \confinv{50}{7}{7} & \confinv{12}{4}{3}\\
        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{118}{10}{11} & \confinv{58}{7}{8} & \confinv{52}{7}{7} & \confinv{8}{3}{3} & \confinv{190}{14}{14} & \confinv{92}{10}{9} & \confinv{85}{9}{9} & \confinv{13}{3}{4}\\
        O & No PISN and pulsational-PISN & \confinv{127}{12}{11} & \confinv{75}{8}{9} & \confinv{43}{6}{7} & \confinv{8}{3}{3} & \confinv{206}{15}{14} & \confinv{121}{11}{10} & \confinv{72}{8}{9} & \confinv{13}{4}{3}\\
        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{185}{14}{13} & \confinv{83}{9}{9} & \confinv{87}{10}{9} & \confinv{15}{4}{4} & \confinv{301}{18}{17} & \confinv{130}{11}{12} & \confinv{145}{12}{12} & \confinv{26}{5}{5}\\
        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{268}{16}{17} & \confinv{92}{10}{9} & \confinv{143}{12}{12} & \confinv{34}{6}{5} & \confinv{427}{21}{21} & \confinv{143}{12}{12} & \boldconfinv{229}{15}{15} & \confinv{55}{8}{7}\\
        R & Black holes receive not natal kick & \confinv{230}{15}{15} & \confinv{91}{10}{9} & \confinv{132}{11}{12} & \confinv{7}{2}{3} & \confinv{373}{20}{19} & \confinv{142}{12}{12} & \confinv{219}{15}{14} & \confinv{12}{4}{3}\\
        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{118}{10}{11} & \confinv{76}{9}{8} & \confinv{34}{6}{6} & \confinv{9}{3}{3} & \confinv{182}{13}{14} & \confinv{112}{10}{11} & \confinv{56}{8}{7} & \confinv{14}{4}{4}\\
        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \boldconfinv{30}{6}{5} & \boldconfinv{6}{3}{2} & \confinv{16}{4}{3} & \confinv{8}{2}{3} & \boldconfinv{49}{7}{7} & \boldconfinv{9}{3}{3} & \confinv{26}{5}{5} & \confinv{13}{3}{4}\\

@@

        - & Minimum rate & \confinv{30}{6}{5} & \confinv{6}{3}{2} & \confinv{2}{1}{2} & \confinv{0}{0}{1} & \confinv{49}{7}{7} & \confinv{9}{3}{3} & \confinv{3}{1}{2} & \confinv{0}{0}{1} \\
        - & Maximum rate & \confinv{321}{18}{18} & \confinv{154}{12}{13} & \confinv{148}{12}{13} & \confinv{35}{6}{6} & \confinv{484}{22}{22} & \confinv{240}{16}{15} & \confinv{229}{15}{15} & \confinv{57}{7}{8} \\

>>>>

        A & Fiducial & \confinv{124}{11}{11} & \confinv{74}{9}{8} & \confinv{42}{6}{7} & \confinv{8}{3}{3} & \confinv{202}{15}{14} & \confinv{117}{10}{11} & \confinv{71}{8}{8} & \confinv{13}{4}{4}\\
        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{94}{10}{10} & \confinv{69}{9}{8} & \confinv{22}{4}{5} & \confinv{3}{2}{2} & \confinv{149}{12}{12} & \confinv{108}{11}{10} & \confinv{37}{6}{6} & \confinv{5}{2}{2}\\
        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{59}{8}{8} & \confinv{47}{7}{7} & \confinv{8}{3}{3} & \confinv{4}{2}{2} & \confinv{96}{10}{9} & \confinv{76}{9}{8} & \confinv{14}{4}{3} & \confinv{7}{3}{2}\\
        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{67}{8}{8} & \confinv{47}{7}{7} & \confinv{7}{2}{3} & \confinv{13}{4}{3} & \confinv{104}{10}{11} & \confinv{71}{8}{8} & \confinv{12}{3}{4} & \confinv{21}{4}{5}\\
        E$^\prime$ & Case BB mass transfer is always unstable & \confinv{90}{10}{9} & \confinv{66}{8}{8} & \confinv{21}{5}{5} & \boldconfinv{3}{2}{1} & \confinv{133}{11}{12} & \confinv{101}{10}{10} & \confinv{29}{5}{5} & \boldconfinv{4}{2}{2}\\
        F & Case BB Unstable + Optimistic CE & \boldconfinv{368}{19}{19} & \boldconfinv{154}{13}{12} & \boldconfinv{198}{14}{14} & \confinv{17}{4}{4} & \boldconfinv{553}{24}{23} & \boldconfinv{238}{15}{16} & \boldconfinv{289}{17}{17} & \confinv{25}{5}{5}\\
        G & CE efficiency $\alpha = 0.1$ & \confinv{40}{6}{6} & \confinv{28}{5}{5} & \boldconfinv{2}{1}{2} & \confinv{10}{3}{3} & \confinv{64}{8}{8} & \confinv{44}{7}{6} & \boldconfinv{3}{1}{2} & \confinv{17}{4}{4}\\
        H & CE efficiency $\alpha = 0.5$ & \confinv{86}{10}{9} & \confinv{58}{7}{8} & \confinv{22}{5}{4} & \confinv{6}{3}{2} & \confinv{136}{12}{11} & \confinv{91}{9}{10} & \confinv{35}{6}{6} & \confinv{10}{3}{3}\\
        I & CE efficiency $\alpha = 2.0$ & \confinv{133}{12}{11} & \confinv{67}{8}{9} & \confinv{38}{6}{6} & \confinv{28}{6}{5} & \confinv{218}{15}{14} & \confinv{109}{10}{11} & \confinv{62}{7}{8} & \confinv{46}{7}{7}\\
        J & CE efficiency $\alpha = 10.0$ & \confinv{78}{9}{9} & \confinv{27}{6}{5} & \confinv{16}{4}{4} & \boldconfinv{35}{6}{6} & \confinv{126}{11}{11} & \confinv{42}{6}{7} & \confinv{27}{6}{5} & \boldconfinv{57}{7}{8}\\
        K & HG donor stars initiating a CE survive CE & \confinv{218}{15}{14} & \confinv{151}{12}{12} & \confinv{57}{8}{7} & \confinv{10}{3}{3} & \confinv{340}{18}{19} & \confinv{229}{15}{15} & \confinv{96}{10}{10} & \confinv{16}{4}{4}\\
        L & Fryer rapid SN remnant mass prescription & \confinv{127}{11}{11} & \confinv{50}{7}{7} & \confinv{70}{8}{8} & \confinv{7}{3}{2} & \confinv{204}{14}{15} & \confinv{76}{8}{9} & \confinv{117}{11}{11} & \confinv{11}{3}{3}\\
        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{133}{11}{12} & \confinv{96}{10}{10} & \confinv{30}{5}{5} & \confinv{7}{2}{3} & \confinv{214}{14}{15} & \confinv{153}{12}{13} & \confinv{50}{7}{7} & \confinv{12}{4}{3}\\
        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{118}{11}{11} & \confinv{58}{8}{8} & \confinv{52}{7}{7} & \confinv{8}{3}{3} & \confinv{189}{13}{14} & \confinv{91}{9}{10} & \confinv{85}{10}{9} & \confinv{14}{4}{3}\\
        O & No PISN and pulsational-PISN & \confinv{126}{11}{12} & \confinv{75}{9}{9} & \confinv{43}{6}{7} & \confinv{8}{3}{3} & \confinv{205}{14}{14} & \confinv{120}{11}{11} & \confinv{72}{8}{9} & \confinv{13}{4}{3}\\
        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{184}{14}{14} & \confinv{82}{9}{9} & \confinv{86}{9}{10} & \confinv{15}{4}{4} & \confinv{300}{17}{17} & \confinv{130}{12}{11} & \confinv{145}{12}{12} & \confinv{26}{6}{5}\\
        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{268}{16}{16} & \confinv{92}{10}{9} & \confinv{143}{12}{12} & \confinv{34}{6}{6} & \confinv{426}{20}{21} & \confinv{142}{11}{12} & \confinv{229}{16}{15} & \confinv{55}{7}{8}\\
        R & Black holes receive not natal kick & \confinv{205}{14}{15} & \confinv{89}{9}{10} & \confinv{109}{11}{10} & \confinv{7}{2}{3} & \confinv{332}{18}{18} & \confinv{140}{12}{12} & \confinv{180}{13}{13} & \confinv{12}{4}{3}\\
        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{118}{11}{11} & \confinv{75}{8}{9} & \confinv{34}{6}{6} & \confinv{9}{3}{3} & \confinv{182}{14}{13} & \confinv{112}{11}{11} & \confinv{56}{8}{7} & \confinv{14}{4}{4}\\
        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \boldconfinv{30}{6}{5} & \boldconfinv{6}{3}{2} & \confinv{15}{3}{4} & \confinv{8}{2}{3} & \boldconfinv{49}{7}{7} & \boldconfinv{9}{3}{3} & \confinv{26}{5}{5} & \confinv{13}{3}{4}\\

@@

        - & Minimum rate & \confinv{30}{6}{5} & \confinv{6}{3}{2} & \confinv{2}{1}{2} & \confinv{3}{2}{1} & \confinv{49}{7}{7} & \confinv{9}{3}{3} & \confinv{3}{1}{2} & \confinv{4}{2}{2} \\
        - & Maximum rate & \confinv{368}{19}{19} & \confinv{154}{13}{12} & \confinv{198}{14}{14} & \confinv{35}{6}{6} & \confinv{553}{24}{23} & \confinv{238}{15}{16} & \confinv{289}{17}{17} & \confinv{57}{7}{8} \\
